---
title: Testing components (with the 0dBm reference in mind)
author: ''
date: '2024-01-21'
slug: testing-components-with-the-0dbm-reference-in-mind
categories: []
tags: []
editor_options: 
  markdown: 
    wrap: 72
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(scales)
library(gt)
```

I am testing some components that I plan to put into the 0dBm reference
for which I now have an untested PCB.

I have the Digilent Analog discovery connected by USB and the "Impedance
Analyzer" adapter. The components are soldered to small adapters with
short leads soldered to fit into the analyzer adapter.

# 4 capacitors

For DC-blocking in the 0dBm 10MHz reference, I have designed with 100nF
capacitors (because I have a lot of them). But the quality of capacitors
this large is not the same that you can get at lower capacitances, my
capacitors at 100nF are either X7R or Y5-something (from a parts-kit).
So my capacitors are (all 100nF):

-   C1: Samsung
    [CL21B104KBNE](https://no.mouser.com/datasheet/2/585/MLCC-1837944.pdf),
    X7R, +/- 10%, 50V, 0805
-   C2: From an AIDETEK kit, X7R, +/- 10%, 50V, 0805
-   C3: From an AIDETEK kit, Y5?, +/- 20%, 50V, 0805
-   C4: Wurth,
    [885012207098](https://datasheet.octopart.com/885012207098-W%C3%BCrth-Elektronik-datasheet-155502646.pdf),
    X7R, +/- 10%, 50V, 0805

```{r message=FALSE, warning=FALSE, include=FALSE}
C1df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "C1_100_compensated.csv"), 
                 comment = "#") |> 
  janitor::clean_names() |>
  mutate(part = "C1")
C2df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "C2_100_compensated.csv"), 
                 comment = "#")  |> 
  janitor::clean_names() |>
  mutate(part = "C2")
C3df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "C3_100_compensated.csv"), 
                 comment = "#")  |> 
  janitor::clean_names() |>
  mutate(part = "C3")
C4df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "C4_100_compensated.csv"), 
                 comment = "#")  |> 
  janitor::clean_names() |>
  mutate(part = "C4")
Cdf <- bind_rows(list(C1df, C2df, C3df, C4df)) |> 
  mutate(impedance = sqrt(real_ohm^2 + imag_ohm^2))
```

I graph the impedance of the different parts

```{r echo=FALSE, message=FALSE, warning=FALSE}
Cdf |> 
  ggplot(aes(x=frequency_hz, y=impedance, color=part)) +
  geom_line() +
    theme_minimal() +
    labs(x = "Frequency [Hz]",
         y = "Impedance [Ohm]",
         title = "4 capacitors",
         color = "Part:") +
  theme(plot.title.position = "plot") +
  scale_x_continuous(trans = "log10", labels = scales::comma) +
  scale_y_continuous(trans = "log10", labels = scales::comma)
```

The resonances (lowest impedance) are at:

```{r echo=FALSE, message=FALSE, warning=FALSE}
Cdf |> group_by(part) |>
  filter(impedance == min(impedance)) |>
  select(c("frequency_hz","impedance")) |> 
  ungroup() |> 
  select(c("part","frequency_hz","impedance")) |>
  gt()
```

So the Aidetek parts are clearly not as good. That the Y5 capacitor is
worse is no surprise, but the X7R are also worse than the Wurth and Samsung parts.
But for DC-blocking, they all seem ok. Here are the impedances at about 10MHz:

```{r echo=FALSE}
Cdf |> group_by(part) |>
  filter(frequency_hz > 10e6) |>
  filter(frequency_hz == min(frequency_hz)) |>
  ungroup() |>
  arrange(part) |>
  select(c("part","impedance")) |>
  gt()
```


# 3 Inductors

The low pass filter is a 7-th order Chebyshev filter intended to sit at 10.5MHz,
and it relies on 1uH inductors. I have three different candidates:

- L1: Kemet [L0805C1R0KSMST](https://connect.kemet.com:7667/gateway/IntelliData-ComponentDocumentation/1.0/download/specsheet/L0805C1R0KSMST), Shielded, Surface Mount Inductor, Ceramic Multilayer (0805).
- L2: TDK [MLZ2012A1R0WT000](https://datasheet.octopart.com/MLZ2012A1R0WT000-TDK-datasheet-155380168.pdf), Multilayer Ferrite  (0805).
- L3: A 1uH from an ebay sample book (0805).


```{r message=FALSE, warning=FALSE, include=FALSE}
L1df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "L1_100_compensated.csv"), 
                 comment = "#") |> 
  janitor::clean_names() |>
  mutate(part = "L1")
L2df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "L2_100_compensated.csv"), 
                 comment = "#") |> 
  janitor::clean_names() |>
  mutate(part = "L2")
L3df <- read_csv(here("content", "post",
                      "2024-01-21-testing-components-with-the-0dbm-reference-in-mind",
                      "L3_100_compensated.csv"), 
                 comment = "#") |> 
  janitor::clean_names() |>
  mutate(part = "L3")
Ldf <- bind_rows(list(L1df, L2df, L3df)) |> 
  mutate(impedance = sqrt(real_ohm^2 + imag_ohm^2))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
Ldf |> 
  ggplot(aes(x=frequency_hz, y=impedance, color=part)) +
  geom_line() +
    theme_minimal() +
    labs(x = "Frequency [Hz]",
         y = "Impedance [Ohm]",
         title = "3 Inductors",
         color = "Part:") +
  theme(plot.title.position = "plot") +
  scale_x_continuous(trans = "log10", labels = scales::comma) +
  scale_y_continuous(trans = "log10", labels = scales::comma)
```

Looking more closely at the values at higher frequencies, let's 
look at the **differences** in impedance from an ideal inductor (which has
$X_L = 2\pi f L$).

```{r echo=FALSE, message=FALSE, warning=FALSE}
Ldf |> mutate(Z_ideal = 2*pi*frequency_hz * 1e-6,
              Z_difference = impedance - Z_ideal,
              Z_d_fraction = (Z_difference / Z_ideal)*100) |>
  filter(frequency_hz > 5e6) |>
  ggplot(aes(x = frequency_hz, y = Z_d_fraction, color=part)) +
  geom_line() +
  theme_minimal() + 
  theme(plot.title.position = "plot") +
  scale_x_continuous(trans = "log10", labels = scales::comma) +
  labs(x = "Frequency [Hz]",
       y = "Difference from ideal inductor [%]",
       title = "Errors at higher frequencies",
       color = "Part:")
  
```

Here it is clear that there is a difference between the parts. The Kemet
inductor (L1) is much better into the tens of MHz. The L2 (TDK) is made
more to work as a Ferrite bead on power lines and such, and it is 
perhaps not so bad. The 1uH from the ebay sample book (L3) does not 
look as good.

